
\documentclass[a4paper, 11pt]{article}
\usepackage[ascii]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{txfonts}
\usepackage{supertabular}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage {geometry}
\geometry{a4paper,top=25mm,left=30mm,right=25mm,bottom=30mm}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



\begin{document}
{\begin{center}\huge\bf openETCS Meeting Minutes\end{center}}

\section{Meeting Information}

\renewcommand{\arraystretch}{1.5}
\begin{supertabular}{m{.2\textwidth}m{.8\textwidth}}
%\hline
Subject & WP7 workshop, evaluation matrix session\\
Date \& time & 2013-04-16, 16:00h--18:00h\\
Location & Munich, site of DB\\
Called up by & Klaus-R\"udiger Hase\\
Participants & cf.~workshop participants\\
Minutes by & Peter Mahlmann\\
%\hline
\end{supertabular}
\renewcommand{\arraystretch}{1.0}


\section{Agenda and Discussion}

\begin{itemize}
\item A decision on the tool to be used in the project will be made at the meeting in Paris on 4th of July.
\item Concerning the review template (O7.1.3) Marielle Petit-Doche expects feedback until 2013-05-03.
\item Slides of tool presentations and the corresponding models will be made available on github.
\item For some of the tools assessors are missing (GNATprove,GOPRR, CORE, Classical B).
\item Concerning the evaluation criteria the following items were discussed (without final decision):
\begin{itemize}
\item Should the individual measures be weighted?
\item Should partners spending more effort (i.e. person months) in the tool chain have more weight on their votes?
\item Since the final decision might be a combination of tools, the tools should be annotated with the respective areas they cover.
\item Non-technical issues like business model, community, and licensing should also be considered in the review process.
\end{itemize}
\item Action items:
\begin{enumerate}
\item A tool artifact matrix should be created.
\item A compliance matrix, presenting the tools and supported methods should be created. Methods identified during the meeting:
documentation, modeling, design, code generation, verification, validation, safety analysis. Armand Nachef volunteered to further elaborate the this list with support of Marc Behrens. Results are expected by 2013-04-26.
\end{enumerate}
\end{itemize}


\section{Notes}
None.
\end{document}
